---
title: "TBT Report"
format: 
  html:
    fig-height: 5
    fig-dpi: 300
    fig-width: 8.8
    fig-align: center
    #theme: theme.scss
server: shiny
execute: 
  echo: false
---

```{r setup, include=FALSE}
#| echo: false
library(pacman)
p_load(tidyverse, shiny, palmerpenguins)


all_measurement_data <- readRDS("all_measurement_data_4report.rds")

dust_data <- read_csv("data/dust_long.csv")
```


```{r}
#| context: server

output$dust_plot <- renderPlot({
  ggplot(dust_data %>% 
         filter(metal == input$metal), aes(x = reading_no, y = conc)) + 
  geom_point() + 
  geom_errorbar( mapping=aes(x=reading_no, 
                                         ymin=conc-error, ymax=conc+error), 
                width=0.2, size=0.2) + 
  facet_wrap(~metal, scales = "free_y") + 
  theme_bw()
})

```

## About the Study


## About the Tiny Beer Team

## Overall Study Results


### Main Result 1
PM2.5 and PM10 concentrations were generally higher in the Brew Pit than in the Taproom

### Main Result 2

Median PM2.5 concentrations were elevated during the scooping (0.033mg/m3), and boiling (0.026mg/m3) stages compared to all other stages (median = 0.006-0.014mg/m3).
```{r}
selectInput(inputId = 'beer',
            label = "Beer",
            choices = c(unique(all_measurement_data$beer_type)))


```

## Main Result 3
PM2.5 and PM10 concentrations varied by beer type (p < 0.001) as well as grain weight (p < 0.001), however, this was likely due to differences in boiling lengths for different beer types as 21% of the variation in log PM2.5 concentrations were explained by the length of boiling on a given day. 

```{r}
# insert boiling stages plot 
```

## Background


### Particulate Matter

### CO2

```{r}
# show sampling data by date with the field log merged in 

```

### What's in the dust? 

```{r}
selectInput(inputId = 'metal',
            label = "Metal",
            choices = c("As", "Ca", "Cd", "Co", "Cr", "Fe", "K", "Mn", "Mo", "Ni",
                 "Pb", "Rb", "Sd", "Sc", "Se", "Sr", "Ti", "Zn", "Zr"))
```


```{r}
plotOutput('dust_plot')

```
## Conclusions